Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-07-19 _tex/manuscript.tex
Built site for gh-pages

\abstract{In current practice, large parts of the contralateral lymph
system are included in the elective clinical target volume (CTV-N) of
oropharyngeal squamous cell carcinoma (OPSCC) patients. Guidelines on
how to define the CTV-N are mostly based on prevalences of nodal
involvement in the different lymph node levels (LNLs) and do not
consider the detailed, individual diagnosis of a patient.

In this work, we present a probabilistic model for bilateral lymphatic
tumor progression in OPSCC. Its aim is to predict the personal risk for
occult disease in any LNL, given the patient's clincal diagnosis,
T-category, and lateralization of the primary tumor. The model
represents each of the LNLs I, II, III, IV, V, and VII of both sides of
the neck as a hidden binary random variable that are connected to the
tumor and among each other via arcs that correspond to spread
probabilities per time-step. These spread probability rates are learned
via Markov chain Monte Carlo (MCMC) sampling from a dataset of 833 OPSCC
patients.

The model is able to describe the data well and may in the future be
used to only include LNLs in a CTV-N that show a risk above a specific
threshold for that particular patient's diagnosis. E.g., it predicts the
risk for occult disease in contralateral LNL II to be below 5\% unless
the tumor crosses the mid-sagittal line.}

@@

When treating head and neck squamous cell carcinomas (HNSCC) with
radiotherapy or surgery, not only the primary tumor and the clinically
detected lymph node metastases are targeted. Per current guidelines,
large volumes of the neck - lymph node levels (LNLs) - are part of the
the elective clinical target volume (CTV-N)
\citep{gregoire_ct-based_2003, gregoire_delineation_2014, gregoire_delineation_2018, eisbruch_intensity-modulated_2002, biau_selection_2019, chao_determination_2002, vorwerk_guidelines_2011, ferlito_elective_2009}.
This is to minimize the risk of regional recurrences due to missed
microscopic disease which cannot be detected by current in-vivo imaging
modalities such as computed tomography (CT), magnetic resonance imaging
(MRI), or positron emission tomography (PET).

Minimizing this risk of missing occult disease in the lymph drainage
region must be balanced against the toxicity related to unnecessary
treatment of healthy tissue.

The aforementioned guidelines for the definition of the CTV-N quantify
this risk via the overall prevalence of lymph node metastases in the
LNLs. Based on this, they recommend extensive irradiation of both sides
of the neck for a majority of patients. However, this prevalence the
guidelines are based on does not take into account the individual state
of tumor progression, which may have a great impact on a patient's
personal risk for occult disease in a given LNL. For example, a patient
with substantial nodal involvement in the ipsilateral side and an
advanced primary tumor that crosses the mid-sagittal plane would receive
extensive elective irradiation of the contralateral LNLs II, III, and
IVa. However, if the patient presented with no clinically detectable
nodal disease (cN0) and only a small, clearly lateralized T1 tumor, the
same contralateral CTV-N would be recommended
\citep{biau_selection_2019}.

To better quantify this personalized risk we have previously developed
an intuitive, probabilistic hidden Markov model
\citep{ludwig_hidden_2021, ludwig_modelling_2023} which was originally
based on a conceptually similar Bayesian network model
\citep{pouymayou_bayesian_2019}. So far, these models were limited to
the ipsilateral side of the neck. The main focus of this work will be to
extend the formalism of these previous works to include risk predictions
for the contralateral side as well. We believe this holds the potential
to greatly reduce the electively irradiated volumes in the contralateral
neck for patients whose individual risk for occult disease in that side
is low. In turn, this may substantially reduce the toxicity from
irradiation and the associated decrease in quality of life.

In the following, we begin by inspecting the dataset the model is built
upon (section~\ref{sec-data}) and from it formulate some properties we
require the bilateral model extension to have
(section~\ref{sec-requirements}).

After that, in section~\ref{sec-unilateral}, we briefly summarize the
original model formalism before we extend it to the contralateral side
starting in section~\ref{sec-ext-to-contra}.

Next, we describe how the model training and the computational
experiments were set up in section~\ref{sec-methods} and present the
results in section~\ref{sec-results}, followed by a closing discussion
(section~\ref{sec-discussion}).

@@

Originally, the only available data of detailed - i.e.~per patient and
per LNL - lymphatic involvement was a reconstructed table from the
findings in \citet{sanguineti_defining_2009}, which included only
ipsilateral nodal involvement for the LNLs I to IV.

To be able to create models for lymphatic tumor progression that include
more LNLs and the contralateral side, we have collected a detailed
dataset of 833 patients with newly diagnosed oropharyngeal squamous cell
carcinomas. It reports the involvement of every patient individually and
per lymph node level in tabular form, in addition to other
clinico-pathological information such as age, T-category, and HPV p16
status.

Their patient records have been collected at four different institutions
and a brief overview over some of their patients' characteristics are
shown in table~\ref{tbl-data-overview}. Note that the data from the
Inselspital Bern and the Centre Léon Bérard only consists of patients
treated with some form of neck dissection. Since this treatment is more
commonly chosen for early T-category patients, they also make up a
larger portion of the respective dataset.

@@

\caption{}\label{T_c3b84}\tabularnewline
\toprule\noalign{}
Institution & Total & Age (median) & Neck Dissection & N0 & Early T-Cat.
& Mid. Ext. \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Institution & Total & Age (median) & Neck Dissection & N0 & Early T-Cat.
& Mid. Ext. \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Centre Léon Bérard & 325 & 60 & 100\% & 19\% & 69\% & 18\% \\
Inselspital Bern & 74 & 61 & 100\% & 18\% & 66\% & 14\% \\
University Hospital Zurich & 287 & 66 & 26\% & 18\% & 52\% & 31\% \\
Vall d\textquotesingle Hebron Barcelona Hospital & 147 & 58 & 5\% & 21\%
& 34\% & 34\% \\

@@

\subsection{Contralateral Involvement Prevalence}\label{sec-data-strat}

@@

\caption{}\label{T_6c7f4}\tabularnewline
\toprule\noalign{}
Parameter & Mean & Std. Dev. \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Parameter & Mean & Std. Dev. \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Mid. ext. probability & 8.16\% & ± 0.48\% \\
ipsi: T ➜ I & 2.80\% & ± 0.26\% \\
ipsi: T ➜ II & 34.89\% & ± 1.40\% \\
ipsi: T ➜ III & 5.45\% & ± 0.66\% \\
ipsi: T ➜ IV & 0.94\% & ± 0.18\% \\
ipsi: T ➜ V & 1.83\% & ± 0.22\% \\
ipsi: T ➜ VII & 2.32\% & ± 0.26\% \\
contra: T ➜ I & 0.29\% & ± 0.09\% \\
contra: T ➜ II & 2.46\% & ± 0.29\% \\
contra: T ➜ III & 0.14\% & ± 0.07\% \\
contra: T ➜ IV & 0.19\% & ± 0.08\% \\
contra: T ➜ V & 0.05\% & ± 0.04\% \\
contra: T ➜ VII & 0.50\% & ± 0.17\% \\
Mixing ⍺ & 33.87\% & ± 4.32\% \\
I ➜ II & 62.50\% & ± 16.69\% \\
II ➜ III & 14.23\% & ± 1.64\% \\
III ➜ IV & 15.86\% & ± 1.93\% \\
IV ➜ V & 14.58\% & ± 3.76\% \\
late T-cat. binom. prob. & 44.98\% & ± 1.99\% \\

@@

\caption{}\label{T_37f78}\tabularnewline
\toprule\noalign{}
T-cat. & ipsi & Mid. ext. & \multicolumn{2}{l}{%
I} & \multicolumn{2}{l}{%
II} & \multicolumn{2}{l}{%
III} & \multicolumn{2}{l}{%
IV} & total \\
& & & n & \% & n & \% & n & \% & n & \% & n \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
T-cat. & ipsi & Mid. ext. & \multicolumn{2}{l}{%
I} & \multicolumn{2}{l}{%
II} & \multicolumn{2}{l}{%
III} & \multicolumn{2}{l}{%
IV} & total \\
& & & n & \% & n & \% & n & \% & n & \% & n \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
early & 0 & False & 0 & 0.00 & 1 & 1.16 & 0 & 0.00 & 0 & 0.00 & 86 \\
early & 0 & True & 0 & 0.00 & 1 & 10.00 & 1 & 10.00 & 0 & 0.00 & 10 \\
early & 1 & False & 1 & 0.53 & 11 & 5.82 & 2 & 1.06 & 1 & 0.53 & 189 \\
early & 1 & True & 1 & 11.11 & 2 & 22.22 & 0 & 0.00 & 0 & 0.00 & 9 \\
early & ≥ 2 & False & 1 & 0.96 & 15 & 14.42 & 3 & 2.88 & 3 & 2.88 &
104 \\
early & ≥ 2 & True & 0 & 0.00 & 3 & 30.00 & 4 & 40.00 & 1 & 10.00 &
10 \\
advanced & 0 & False & 0 & 0.00 & 2 & 5.88 & 0 & 0.00 & 0 & 0.00 & 34 \\
advanced & 0 & True & 0 & 0.00 & 3 & 12.50 & 0 & 0.00 & 0 & 0.00 & 24 \\
advanced & 1 & False & 0 & 0.00 & 3 & 4.55 & 0 & 0.00 & 0 & 0.00 & 66 \\
advanced & 1 & True & 1 & 1.64 & 18 & 29.51 & 5 & 8.20 & 1 & 1.64 &
61 \\
advanced & ≥ 2 & False & 4 & 5.26 & 16 & 21.05 & 7 & 9.21 & 4 & 5.26 &
76 \\
advanced & ≥ 2 & True & 3 & 3.80 & 46 & 58.23 & 18 & 22.78 & 8 & 10.13 &
79 \\

@@

\section{Marginalizing Beta Posteriors over
Unknowns}\label{marginalizing-beta-posteriors-over-unknowns}

\begin{longtable}[]{@{}llll@{}}

\caption{\label{tbl-data-unknowns}Combinations of midline extension
status and state of contralateral LNL II for early T-category patients.}

\toprule\noalign{}
Midline Extension & no & yes & unknown \\
contra LNL II & & & \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
healthy & 352 & 23 & 59 \\
involved & 27 & 6 & 6 \\
total & 379 & 29 & 65 \\

In section~\ref{sec-prevalence} we explained that we compare the
predicted prevalence of an involvement pattern under a scenario to a
beta posterior over the ``true'' prevalence given the observations in
the data. However, our data contains incomplete observations, especially
regarding the tumor's midline extension. This information is not present
for a large group of 85 patients, most of which treated at the Centre
Léon Bérard in France.

To account for this missing information and plot the correct posteriors
over the data prevalence, we need to marginalize over the possible
combinations of matching involvement patterns and selected patients
under a scenario. For example, we have only 29 early T-category patients
with midline extension. But for an additional 65 patients we do not know
whether the tumor crossed the mid-sagittal plane. If we now want to
compute the prevalence of contralateral LNL II invovlement for these
early T-category patients with midline extension, then we need to
account for the possibility that we are missing information.

In table~\ref{tbl-data-unknowns} we show the combinations of the midline
extension status and state of the contralateral LNL II. Using only
available information, we would get to 6 out of 29 patients for the
prevalence of contralateral LNL II invovlement among the early
T-category patients with midline extension. But the column with the
``unknown'' numbers suggests that the true prevalence could range from 6
out of 29 + 59 (7\%) up to 12 out of 29 + 6 (34\%). We assume that every
one of the possible combinations has the same a priori probability
(uniform prior) but we do need to account for permutations via the
binomial factor. In general, let us say we have \(n\) patients with
midline extension, of which \(k\) harbor metastases in the contralateral
LNL II. And we have \(m\) patients with unknown midline extension, of
which \(\ell\) presented with diasease in contralateral LNL II, then the
posterior distribution - marginalized over the unknown data - over the
true prevalence \(x \in \left[ 0, 1 \right]\) is given by:

\[
p(x \mid n, k, m, \ell, \alpha, \beta) = \left[ \frac{1}{m} \sum_{i=0}^m \frac{1}{\min(i,\ell)} \sum_{j=0}^{\min(i,\ell)} \frac{P(i, j \mid x )}{\binom{n}{k}} \right] \cdot P(n, k \mid x) \cdot \frac{1}{\operatorname{B}(\alpha, \beta)} x^\alpha (1-x)^\beta
\]

Note the two binomial likelihoods: one being marginalized over and one
acting implicitly as a prior to the summed terms. This role of the
likelihood over the data with known midline extension as a prior to the
part where that data is missing corrects for the fact that there are
highly unlikely combinations among those we marginalize over. E.g.,
expecting that exactly those 6 patients with contralateral LNL II
involvemnt are also coincidentially the only ones of the 65 with a tumor
crossing the mid-sagittal line is very unlikely. This is accounted for
by the fact that this possibility has only one permutation and it is
weakened by the likelihood over the data with known midline extension.
With a uniform prior beta distribution (\(\alpha=1\) and \(\beta=1\)),
the above simplifies to:

\[
p(x \mid n, k, m, \ell) = \left[ \frac{1}{m} \sum_{i=0}^m \frac{1}{\min(i,\ell)} \sum_{j=0}^{\min(i,\ell)} \binom{n+i}{k+j} x^j (1 - x)^{i-j} \right] \cdot x^{k+1} (1 - x)^{n-k+1}
\]

We have plotted this marginal in figure~\ref{fig-model-marginal-pdf}
(blue curve) and the terms that make up the above sum (light red
curves). Note that we weighted the plotting opacity with the number of
permutations each of the possible combinations has. The marginal is
compared against the ``naive'' beta posterior that only takes the data
into account for which midline extension is available (green curve).

\includegraphics[width=0.5\textwidth,height=\textheight]{manuscript_files/mediabag/figures/fig-model-marginal-pdf.pdf}

\caption{\label{fig-model-marginal-pdf}Posterior distributions over the
data prevalence for contralateral LNL II involvement under the scenario
of early T-category and midline extension. The green beta distribution
shows this prevalence for those patients for which midline extension is
known. While the blue PDF is a marginal distribution summed over all
possible combinations, which are shown in shades of red. The more
permutations a particular combination has, the more opaque it is
plotted.}

The distribution that marginalizes over the unknown midline extension
cases is shifted towards a lower prevalence. This makes intuitive sense:
With only 6 patients among the 65 with unknown midline extension status,
the upper bound for the prevalence has moved down compared to 6 out of
29.

We chose to compare our model against such corrected prevalence
posteriors, because the model, too, is capable of marginalizing over
unknown midline extension in the data. It would therefore be inaccurate
to compare the model trained with the full dataset to only that part of
the patient cohort where the tumor lateralization was recorded.

>>>>

\abstract{Purpose: According to current guidelines for elective nodal
irradiation of oropharyngeal squamous cell carcinoma (OPSCC) patients,
large parts of the contralateral lymphatic system are included in the
elective clinical target volume (CTV-N), even for lateralized tumors
without clinical lymph node involvement in the contralateral neck. In
this work, we present a probabilistic model for bilateral lymphatic
tumor progression in OPSCC to predict the personal risk for occult
disease in any lymph node level (LNL), given the patient's clinical
lymph node involvement, T-stage, and lateralization of the primary
tumor.

Methods: We extend a hidden markov model for lymphatic tumor
progression, which was previously developed for ipsilateral lymph node
involvement, to the contralateral neck. The model represents each of the
LNLs I, II, III, IV, V, and VII of both sides of the neck as a hidden
binary random variable with states healthy and involved. LNLs are
connected to the tumor and among each other via arcs that correspond to
spread probabilities. These spread probability rates are learned via
Markov chain Monte Carlo (MCMC) sampling from a dataset of 833 OPSCC
patients.

Results: The model is able to describe the data on lymph node
involvement well with a small number of interpretable parameters.
Midline extension of the primary tumor is the main risk factor for
contralateral involvement. In addition, the risk of occult metastases in
contralateral lymph node level increases with more advanced T-stage and
more severe ipsilateral involvement. The probability of involvement in
contralateral level III is very low if the upstream level II is
clinically negative. Similarly, the probability of involvement in
contralateral level IV is very low if the upstream level III is
clinically negative.

Conclusions: The model may guide personalized volume reduction of the
elective CTV-N. It suggests that the contralateral neck may be spared
from elective irradiation for lateralized tumors not crossing the
midline. In patients with primary tumors crossing the midline but
clinically negative contralateral neck, the contralateral elective
irradiation may be limited to level II.}

@@

When treating head and neck squamous cell carcinomas (HNSCC) with
radiotherapy or surgery, not only the primary tumor and the clinically
detected lymph node metastases are targeted. Per current guidelines,
large volumes of the neck are part of the the elective clinical target
volume (CTV-N)
\citep{gregoire_ct-based_2003, gregoire_delineation_2014, gregoire_delineation_2018, eisbruch_intensity-modulated_2002, biau_selection_2019, chao_determination_2002, vorwerk_guidelines_2011, ferlito_elective_2009}.
This is to minimize the risk of regional recurrences due to untreated
microscopic disease which cannot be detected by current in-vivo imaging
modalities such as computed tomography (CT), magnetic resonance imaging
(MRI), or positron emission tomography (PET). However, minimizing the
risk of missing occult disease in the lymph drainage region must be
balanced against the toxicity related to unnecessary treatment of
healthy tissue.

The aforementioned guidelines for the definition of the CTV-N are based
on anatomically defined lymph node levels (LNL)
\citep{gregoire_delineation_2014} and the overall prevalence of lymph
node metastases in the LNLs. Based on this, they recommend extensive
irradiation of both sides of the neck for a majority of patients.
However, this prevalence the guidelines are based on does not take into
account an individual patient's state of tumor progression, which may
have a great impact on a patient's personal risk for occult disease in a
given LNL. For example, a patient with substantial nodal involvement in
the ipsilateral side and an advanced primary tumor that crosses the
mid-sagittal plane would receive extensive elective irradiation of the
contralateral LNLs II, III, and IVa. However, if the patient presented
with no clinically detectable nodal disease (cN0) and only a small,
clearly lateralized T1 tumor, the same contralateral CTV-N would be
recommended \citep{biau_selection_2019}.

To better quantify this personalized risk of occult disease we have
previously developed an intuitive, probabilistic hidden Markov model
\citep{ludwig_hidden_2021, ludwig_modelling_2023} which was originally
based on a conceptually similar Bayesian network model
\citep{pouymayou_bayesian_2019}. So far, these models were limited to
the ipsilateral side of the neck. The main contribution of this work
will be to extend the formalism to include risk predictions for the
contralateral side as well. We believe this holds the potential to
reduce the electively irradiated volumes in the contralateral neck for
patients whose individual risk for occult disease is low. In turn, this
may substantially reduce the toxicity from irradiation and the
associated decrease in quality of life.

The main contributions of this paper are as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  In section section~\ref{sec-data} we present a multi-centric dataset
  on lymph node involvement in 833 OPSCC patients. Based on the dataset
  the main risk factors for contralateral lymph node involvement are
  identified and the requirements for the bilateral model extension are
  described (section~\ref{sec-requirements}).
\item
  In section~\ref{sec-ext-to-contra} we present a bilateral HMM of
  lymphatic progression that accounts for the T-stage lateralization of
  the primary tumor as well as clinical involvement as risk factors for
  occult contralateral involvement. In section~\ref{sec-methods} we
  describe how the model training and the computational experiments were
  set up.
\item
  In the results in section~\ref{sec-results}, we demonstrate that the
  model is able to describe the patterns of contralateral lymph node
  involvement observed in the dataset, and we apply the model to
  estimating risk of occult disease for typical patients. In
  section~\ref{sec-discussion}, implications for volume-deescalated
  radiotherapy are discussed.
\end{enumerate}

@@

To be able to create models for lymphatic tumor progression that
includes all relevant LNLs including the contralateral side, we have
collected a detailed dataset of 833 patients with newly diagnosed
oropharyngeal squamous cell carcinomas. It reports the lymph node
involvement per LNL of every patient individually in tabular form, in
addition to other primary tumor and patient characteristics such as
T-category, subside, and lateralization of the primary tumor, and HPV
p16 status. Their patient records have been collected at four different
institutions and a brief overview over some of their patients'
characteristics are shown in table~\ref{tbl-data-overview}. The data
from the Inselspital Bern and the Centre Léon Bérard only consists of
patients who received a neck dissection. Since this treatment is more
commonly chosen for early T-category patients, they also make up a
larger portion of the respective dataset. The majority of patients from
the University Hospital Zürich and the Vall d'Hebron Barcelona Hospital
was treated with definitive radiotherapy.

@@

\caption{}\label{T_b5301}\tabularnewline
\toprule\noalign{}
Institution & Total & Age (median) & Neck Dissection & N0 & Early T-Cat.
& Mid. Ext. \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Institution & Total & Age (median) & Neck Dissection & N0 & Early T-Cat.
& Mid. Ext. \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Centre Léon Bérard & 325 & 60 & 100\% & 19\% & 69\% & 18\% \\
Inselspital Bern & 74 & 61 & 100\% & 18\% & 66\% & 14\% \\
University Hospital Zurich & 287 & 66 & 26\% & 18\% & 52\% & 31\% \\
Vall d\textquotesingle Hebron Barcelona Hospital & 147 & 58 & 5\% & 21\%
& 34\% & 34\% \\

@@

\subsection{Patterns of Contralateral Involvement}\label{sec-data-strat}

@@

\caption{}\label{T_6f0e6}\tabularnewline
\toprule\noalign{}
Parameter & Mean & Std. Dev. \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Parameter & Mean & Std. Dev. \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Mid. ext. probability & 8.16\% & ± 0.48\% \\
ipsi: T ➜ I & 2.80\% & ± 0.26\% \\
ipsi: T ➜ II & 34.89\% & ± 1.40\% \\
ipsi: T ➜ III & 5.45\% & ± 0.66\% \\
ipsi: T ➜ IV & 0.94\% & ± 0.18\% \\
ipsi: T ➜ V & 1.83\% & ± 0.22\% \\
ipsi: T ➜ VII & 2.32\% & ± 0.26\% \\
contra: T ➜ I & 0.29\% & ± 0.09\% \\
contra: T ➜ II & 2.46\% & ± 0.29\% \\
contra: T ➜ III & 0.14\% & ± 0.07\% \\
contra: T ➜ IV & 0.19\% & ± 0.08\% \\
contra: T ➜ V & 0.05\% & ± 0.04\% \\
contra: T ➜ VII & 0.50\% & ± 0.17\% \\
Mixing ⍺ & 33.87\% & ± 4.32\% \\
I ➜ II & 62.50\% & ± 16.69\% \\
II ➜ III & 14.23\% & ± 1.64\% \\
III ➜ IV & 15.86\% & ± 1.93\% \\
IV ➜ V & 14.58\% & ± 3.76\% \\
late T-cat. binom. prob. & 44.98\% & ± 1.99\% \\

@@

\caption{}\label{T_a95ce}\tabularnewline
\toprule\noalign{}
T-cat. & ipsi & Mid. ext. & \multicolumn{2}{l}{%
I} & \multicolumn{2}{l}{%
II} & \multicolumn{2}{l}{%
III} & \multicolumn{2}{l}{%
IV} & total \\
& & & n & \% & n & \% & n & \% & n & \% & n \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
T-cat. & ipsi & Mid. ext. & \multicolumn{2}{l}{%
I} & \multicolumn{2}{l}{%
II} & \multicolumn{2}{l}{%
III} & \multicolumn{2}{l}{%
IV} & total \\
& & & n & \% & n & \% & n & \% & n & \% & n \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
early & 0 & False & 0 & 0.00 & 1 & 1.16 & 0 & 0.00 & 0 & 0.00 & 86 \\
early & 0 & True & 0 & 0.00 & 1 & 10.00 & 1 & 10.00 & 0 & 0.00 & 10 \\
early & 1 & False & 1 & 0.53 & 11 & 5.82 & 2 & 1.06 & 1 & 0.53 & 189 \\
early & 1 & True & 1 & 11.11 & 2 & 22.22 & 0 & 0.00 & 0 & 0.00 & 9 \\
early & ≥ 2 & False & 1 & 0.96 & 15 & 14.42 & 3 & 2.88 & 3 & 2.88 &
104 \\
early & ≥ 2 & True & 0 & 0.00 & 3 & 30.00 & 4 & 40.00 & 1 & 10.00 &
10 \\
advanced & 0 & False & 0 & 0.00 & 2 & 5.88 & 0 & 0.00 & 0 & 0.00 & 34 \\
advanced & 0 & True & 0 & 0.00 & 3 & 12.50 & 0 & 0.00 & 0 & 0.00 & 24 \\
advanced & 1 & False & 0 & 0.00 & 3 & 4.55 & 0 & 0.00 & 0 & 0.00 & 66 \\
advanced & 1 & True & 1 & 1.64 & 18 & 29.51 & 5 & 8.20 & 1 & 1.64 &
61 \\
advanced & ≥ 2 & False & 4 & 5.26 & 16 & 21.05 & 7 & 9.21 & 4 & 5.26 &
76 \\
advanced & ≥ 2 & True & 3 & 3.80 & 46 & 58.23 & 18 & 22.78 & 8 & 10.13 &
79 \\

@@
